---
title: "Water Pump Analysis"
output: html_notebook
---



```{r}
set.seed(42)
water <- read.csv("waterTraining.csv")
trainLabels <- read.csv("waterTrainingLabels.csv")
test <- read.csv("waterTest.csv")
```


```{r}
dim(water)
colnames(water)
head(water)
```

We are trying to predict whether a water pipe is functional, non-functional, or functional but needs repair.

```{r}
unique(trainLabels$status_group)
length(unique(water$installer))  # checking number of unique installers - too many to add all covariates
                                 # could maybe group them together though
```


```{r}
#str(water)
which_numeric = sapply(1:ncol(water), 
                       function(x) is.numeric(water[,x]) &&
                         all(is.finite(water[,x])))

str(water[, which_numeric][, -1])  # getting rid of id and seeing just numeric columns
```

After investigating histograms of the numerical variables, none of them really resemble a normal distribution, and thus, perhaps logistic regression will produce desired results (though there are 3 categories for the response, not binary).

Let's check again for any missing data

```{r}
any(apply(water, 2, function(x) any(is.na(x) | is.infinite(x))))  # No N/A or Inf!
```

Seems too good to be true.  Maybe encoded as a number, such as zero?

```{r}
NZero <- data.frame(ColName = c("0", "0"), numZeros = c(0,0))
for (col in colnames(water)) {
  nzero <- sum(water[, col] == 0)
  NZero <- rbind(NZero, data.frame(ColName = c(col), numZeros = c(nzero)))
}
NZero <- NZero[3:nrow(NZero),]
NZero
```


```{r}
dim(water)
head(water[, "amount_tsh"])
```

We need to get rid of factors with too many levels, as these take up too many degrees of freedom for our predictions, and will help us with variable reduction.

```{r}
boundary <- 21
count <- 0
indexes <- c()
for (colIndex in 1:(ncol(water))) {
  if (length(levels(water[, colIndex])) > boundary) {
    count <- count + 1
    indexes <- c(indexes, colIndex)
  }
}
count
colnames(water[, indexes])
```


```{r}
length(levels(water[, "installer"]))  # Thought could be useful but too many
redWater <- water[, -indexes]
redWater <- subset(redWater, select = -c(recorded_by))   # Factor with only 1 level
```


```{r}
#str(redWater)
```

There are many categorical predictors, and after looking again at the structure of the dataset we realize that many of them are duplicates of others.  By this we mean that some columns are exactly the same, or that some predictors just group some of the labels together, but represent the same measurement.  We examined each variable using the table() R command, to see all of the unique label names and counts and compare them with their similar counterparts.  In most cases, we chose to keep the predictor with less labels (or the one that grouped together more categories) so that there will be less parameter estimates, saving important degrees of freedom.  However, if we thought that the labels should not have been grouped together, and that their responses would vary significantly, we chose to keep the predictor with more variables.  The choices are summarized in the table below.

| Removed predictors                        | Represented By        |
|:-----------------------------------------:|:---------------------:|
| extraction_type, extraction_type_group    | extraction_type_class |
| management                                | management_group      |
| payment_type                              | payment               |
| water_quality                             | quality_group         |
| quantity_group                            | quantity              |
| source_type, source_class                 | source                |
| waterpoint_type                           | waterpoint_type_group |

```{r}
# source_type and source_class is shown in source column, but
#    we need to combine "unknown" category into "other"
redWater <- subset(redWater, select = -c(extraction_type, 
                                         extraction_type_group,
                                         management,
                                         payment_type,
                                         water_quality,
                                         quantity_group,
                                         source_type,
                                         source_class,
                                         waterpoint_type))
dim(redWater)
```

```{r}
redWater$source[redWater$source == "unknown"] <- "other"
levels(redWater$source) <- droplevels(redWater$source)
dim(redWater)
```

```{r}
# 3 columns that have blank entries
sum(redWater$public_meeting == "")      # 3,334 blanks
sum(redWater$scheme_management == "")   # 3,877 blanks
sum(redWater$permit == "")              # 3,056 blanks
```

Saw one person online that dropped public_meeting and permit, and
filled scheme_management with "other"
https://github.com/vaibhavshukla182/Tanzania-Water-Supply/blob/master/data_visualisation_and_cleaning.ipynb

```{r}
# how many rows have any blanks?
sum(redWater$public_meeting == "" | redWater$scheme_management == "" | redWater$permit == "")     # 9,559 -> too many to just remove
```

```{r}
table(redWater$public_meeting)      # not obvious... maybe False?
table(redWater$scheme_management)   # None? Other?
table(redWater$permit)              # not obvious... maybe False?
```


```{r}
# write reduced data to file
write.csv(redWater, "ReducedWaterTraining.csv")
```

