---
title: "R Notebook"
date: April 12, 2019
output: html_notebook
---

Load the packages:

```{r}
library(ggplot2)
library(dplyr)
require(nnet)

#install.packages('caret')
#install.packages('e1071')
library(caret)
library(e1071)
```

Load the data:

```{r}
#setwd("~/1_wiliiam_and_mary/classes/DataMining/DataMining-Assignments/TeamProject")
clean_data <- read.csv("../Data/ReducedWaterTraining.csv")
clean_data <- clean_data[-1]
trainLabels <- read.csv("../Data/waterTrainingLabels.csv")
head(clean_data, 2)
```

Merge the dataset with the labels set:


```{r}
clean_data_1 <- merge(clean_data, trainLabels)
colnames(clean_data_1)
```


Start splitting the data into training and test sets:

```{r}
set.seed(4321)
randomized = sample(1:nrow(clean_data))
train_set = randomized[1:floor(length(randomized)/3)]
test_set = setdiff(randomized,train_set)
train_d = clean_data_1[train_set,]
test_d = clean_data_1[test_set,]
head(train_d, 2)
head(test_d, 2)
```


Model with all variables included (excluding the id)

```{r}
train_model <- multinom(status_group ~ ., data = train_d[, -1])
```

Get training accuracy information:

```{r}
train_pred = predict(train_model)
#summary(train_pred)

# use caret package to see the confusion matrix
train_conf = confusionMatrix(data=train_pred,reference=train_d$status_group)
train_conf
# Old: 72.36% accuracy
# New: 73.41%

```


```{r}
test_pred = predict(train_model,newdata=test_d)
test_conf = confusionMatrix(data=test_pred,reference=test_d$status_group)
test_conf

# Old: 71.59% accuracy
# New: 72.68%
                    
```


```{r}
train_err = mean(train_pred!=train_d$status_group)
test_err = mean(test_pred!=test_d$status_group)

train_err
test_err
```

Now try on the full training set:

```{r}
log_model <- multinom(status_group ~ ., data = clean_data_1[, -1])
```

Get accuracy information:
```{r}
log_pred = predict(log_model)
#summary(train_pred)

# use caret package to see the confusion matrix
log_conf = confusionMatrix(data=log_pred, reference=clean_data_1$status_group)
log_conf
# 73.22% accuracy
```

Try to get predictions for the complete Test data:

```{r}
clean_test <- read.csv("../Data/ReducedWaterTest.csv")
head(clean_test,2)
```

```{r}
test_log_pred = predict(log_model, newdata=clean_test)
summary(test_log_pred)
```

Add the predicted labels to the test data set
```{r}
clean_test$status_group <- test_log_pred
head(clean_test, 2)
```


```{r}
# write new label data to file
write.csv(clean_test, "../Data/Label_Log_1.csv")
```

Got score of 0.7143 for the competition submission. 
