\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage,amsmath,amssymb}
\usepackage{graphicx,caption, float}
\usepackage{fancyvrb,placeins,lscape, arydshln}
\usepackage[title]{appendix}
\usepackage{newtxtext,newtxmath, url}
\RecustomVerbatimCommand{\VerbatimInput}{VerbatimInput}{fontsize=\scriptsize}
\newenvironment{changemargin}[2]{%

\begin{list}{}{%
\setlength{\topsep}{0pt}%
\setlength{\leftmargin}{#1}%
\setlength{\rightmargin}{#2}%
\setlength{\listparindent}{\parindent}%
\setlength{\itemindent}{\parindent}%
\setlength{\parsep}{\parskip}%
}%
\item[]}{\end{list}}

\title{\textit{Get Pumped:} Water Table Data}
\author{Ethan Buck, Leyli Garryyeva, Gergana Gospodinova, and Xin Zhang}
\date{\today}

\begin{document}

\maketitle

\section{Problem Description}
This project stems from finding a data set from a competition on DrivenData.  The competition is called ``Pump it Up: Data Mining the Water Table'', and provides a data set with different water points.  There are six different types of water points:

\begin{enumerate}
    \item Cattle Trough
    \item Communal Standpipe
    \item Dam
    \item Hand Pump
    \item Improved Spring
    \item Other
\end{enumerate}

The goal is to accurately predict the operating condition of these water points located in Tanzania.  There are three different classes for this response variable, which are

\begin{enumerate}
    \item functional
    \item functional needs repair
    \item non functional
\end{enumerate}

Thus, this is a classification problem.  There are 39 different predictors for this data set, nine of which are continuous covariates.  Early data exploration reveals that none of these continuous covariates appear to resemble a normal distribution, and thus LDA and QDA most likely are not suitable choices.  However, an adapted logistic regression may prove to be fruitful in this analysis, as well as a potential random forest model.  KNN classification may be suitable as well, since there are a large number of training observations (59,400).

Section \ref{dataClean} will discuss the data cleaning process.  Exploratory plots are shown in Section \ref{explore}.  The KNN analysis follows in Section \ref{knn}.  Section \ref{logistic} goes through the logistic regression results, and Section \ref{randForest} explains the results from random forests.

\include{DataClean}

\include{ExplorePlots}

\include{KNN}

\include{Logistic}

\include{RandForest}

\section{Conclusions}

\newpage
\section{Appendix}


%The data set can be found online at \\ %\url{https://www.drivendata.org/competitions/7/pump-it-up-data-mining-the-water-table/page/23/}

\end{document}
